Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-23 manuscript.Rmd
Peer review from Manuel Vazquez

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4) #Don't know why, but this wasn't immediately working
library(lmerTest)
library(rio)
```

@@

```{r}
table1
```

@@

sjPlot::tab_model(SRMdat1) #this is really cool
```

@@

sjPlot::tab_model(normEASRM, diffEASRM)
```

@@

>>>>

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
library(rio)
```

@@

```{r}
# Peer Review: Perhaps you can use a package like the "gt" package to format the table 
table1
```

@@

sjPlot::tab_model(SRMdat1)
```

@@

sjPlot::tab_model(normEASRM, diffEASRM)

#PEER REVIEW: I notice you are writing very similar models across different outcomes, is there an option to create a function and reduce some of the repetitive code?
```

@@

#PEER REVIEW: Random note, I used to work with Dr. Karyn Lewis when she was at Education Northwes :)
